\input{../common}
\input{../bibliography}

\begin{document}
  %<*content>
  \ranking{1987}

  $238$ admis pour cette session.

  \begin{xltabular}{\linewidth}{|l|X|}
    \hline
    \textbf{Rang} & \textbf{Candidat} \\
    \hline
    $202$ & ABADIE MICHEL \\
    \hline
    $218$ & AIME PIERRE \\
    \hline
    $32$ & ALBOUY ALAIN \\
    \hline
    $107$ & AMIOT GILLES \\
    \hline
    $185$ & ANGIONI DANIEL \\
    \hline
    $149$ & ASSAYAG ISAAC \\
    \hline
    $190$ & AUDEOUD LORETTE \\
    \hline
    $218$ & AUDIN PIERRE \\
    \hline
    $108$ & BARRUYER ANNE \\
    \hline
    $165$ & BEIX AGNÈS \\
    \hline
    $77$ & BELLIER ANNE \\
    \hline
    $138$ & BENSAID DANIEL \\
    \hline
    $88$ & BERAUD PIERRE \\
    \hline
    $195$ & BERGER THIERRY \\
    \hline
    $63$ & BERNARD JEAN-PHILIPPE \\
    \hline
    $57$ & BERNIS LAURENT \\
    \hline
    $202$ & BIDALLIER DOMINIQUE \\
    \hline
    $13$ & BIGEARD ISABELLE \\
    \hline
    $195$ & BILDSTEIN ODILE \\
    \hline
    $108$ & BLANC NICOLAS \\
    \hline
    $65$ & BLANCHARD ANNE \\
    \hline
    $201$ & BLANCHARD JEAN \\
    \hline
    $215$ & BONET JOSÉ \\
    \hline
    $135$ & BONNARD CHRISTIAN \\
    \hline
    $22$ & BOUJU SERGE \\
    \hline
    $202$ & BOURGET ÉP. DESCHAMPS BRIGITTE \\
    \hline
    $3$ & BOUSCH THIERRY \\
    \hline
    $125$ & BRACHET JACQUES \\
    \hline
    $188$ & BRIGHI BERNARD \\
    \hline
    $60$ & BROUILLAUD STÉPHANE \\
    \hline
    $23$ & BRUGIÈRE PIERRE \\
    \hline
    $35$ & BRUN THIERRY \\
    \hline
    $155$ & BUYSE ÉP. BOUTON PASCALE \\
    \hline
    $218$ & CABAU PATRICK \\
    \hline
    $130$ & CACHET GÉRARD \\
    \hline
    $213$ & CACHEZ ÉP. DE VATHAIRE JOCELYNE \\
    \hline
    $119$ & CAPELLE CHRISTOPHE \\
    \hline
    $79$ & CAREL MARION \\
    \hline
    $58$ & CASTELL FABIENNE \\
    \hline
    $17$ & CATTO ISABELLE \\
    \hline
    $130$ & CHANTELOUP MARC \\
    \hline
    $115$ & CHARDIN MARC \\
    \hline
    $165$ & CHATEIGNER MICHEL \\
    \hline
    $186$ & CHESNEAU XAVIER \\
    \hline
    $81$ & CHEVALIER JEAN-YVES \\
    \hline
    $218$ & CIEUTAT PHILIPPE \\
    \hline
    $202$ & CLARET ANNIE \\
    \hline
    $91$ & CLÉMENT FRANÇOIS \\
    \hline
    $38$ & CLIGNIEZ GÉRARD \\
    \hline
    $168$ & COGGIA JEAN \\
    \hline
    $14$ & COHEN SERGE \\
    \hline
    $42$ & CONTEJEAN EVELYNE \\
    \hline
    $39$ & COQUET BÉATRICE \\
    \hline
    $202$ & COURBOT BERNARD \\
    \hline
    $88$ & CRANSAC MICHEL \\
    \hline
    $145$ & CREPIN DOMINIQUE \\
    \hline
    $118$ & CRISTOFOL MICHEL \\
    \hline
    $125$ & CROZET PASCAL \\
    \hline
    $77$ & DAMIN WALTER \\
    \hline
    $181$ & DARDIE JEAN-MICHEL \\
    \hline
    $145$ & DAUDE HERVÉ \\
    \hline
    $45$ & DAUMER FRANCK \\
    \hline
    $7$ & DEBUSSCHE ARNAUD \\
    \hline
    $108$ & DEDE ALEXANDRE \\
    \hline
    $86$ & DELAGE CHRISTINE \\
    \hline
    $83$ & DELCROIX MARIE-FRANÇOIS \\
    \hline
    $173$ & DEMONCHY JEAN-PIERRE \\
    \hline
    $25$ & DENIS LAURENT \\
    \hline
    $152$ & DEPIERRE ÉP. ZAHM SIMONE \\
    \hline
    $188$ & DERUELLE GILES \\
    \hline
    $125$ & DESMARS ÉP. HERVÉ ANNE \\
    \hline
    $7$ & DESVILLETTES LAURENT \\
    \hline
    $75$ & DIARTE JÉRÔME \\
    \hline
    $199$ & DIOT MICHEL \\
    \hline
    $61$ & DOMINGUEZ SOPHIE \\
    \hline
    $215$ & DREY FRANCIS \\
    \hline
    $130$ & DROUIN CHRISTIAN \\
    \hline
    $68$ & DUCRET MYRIAM \\
    \hline
    $67$ & DUCROT PHILIPPE \\
    \hline
    $208$ & DUFFAUT YVAN \\
    \hline
    $97$ & DUGOWSON STÉPHANE \\
    \hline
    $114$ & DUPONT YVES \\
    \hline
    $101$ & DUTARTE PHILIPPE \\
    \hline
    $175$ & EL ANHARI AHMED \\
    \hline
    $142$ & ENGEL DANIEL \\
    \hline
    $47$ & ET BAPATRICIO SIMONETTA \\
    \hline
    $35$ & FABRE SOPHIE \\
    \hline
    $17$ & FAUVEAU JEAN-CHRISTOPHE \\
    \hline
    $213$ & FERRY PIERRE \\
    \hline
    $19$ & FINKEL OLIVIER \\
    \hline
    $88$ & FLAHAUT ISABELLE \\
    \hline
    $39$ & FOUCAULT ERIC \\
    \hline
    $235$ & FOUGERONT JACQUES \\
    \hline
    $218$ & FRUGIER GÉRARD \\
    \hline
    $152$ & GAUDY CATHERINE \\
    \hline
    $184$ & GIL BERNARD \\
    \hline
    $218$ & GIRARD PIERRE \\
    \hline
    $155$ & GRAS HERVÉ \\
    \hline
    $178$ & GREVIN CATHERINE \\
    \hline
    $16$ & GRUAIS ISABELLE \\
    \hline
    $63$ & GUEGAN LAURE \\
    \hline
    $125$ & GUENIER LUC \\
    \hline
    $130$ & HAMEL PATRICK \\
    \hline
    $21$ & HARGE GILLES \\
    \hline
    $31$ & HARTMANN FRANÇOIS \\
    \hline
    $130$ & HATCHVEL FRANÇOISE \\
    \hline
    $47$ & HERVÉ LOIC-NOËL \\
    \hline
    $170$ & HUBERT ÉP. ALEXANDRE CATHERINE \\
    \hline
    $181$ & HUET MICHEL \\
    \hline
    $70$ & HUPPERT ÉP. WILL ANNE \\
    \hline
    $6$ & IAGOLNITZER LAURENT \\
    \hline
    $125$ & JAN ALAIN \\
    \hline
    $170$ & JAUME CLAIRE \\
    \hline
    $68$ & JOLLET MARIE \\
    \hline
    $193$ & JOSEPH ISABELLE \\
    \hline
    $101$ & JOUAN PATRICK \\
    \hline
    $1$ & JOUINI ELYER \\
    \hline
    $208$ & JULLIEN ROGER \\
    \hline
    $215$ & KERMARO ANNE \\
    \hline
    $47$ & KOELBLEN LOUIS \\
    \hline
    $53$ & KOLEV BORIS \\
    \hline
    $12$ & KOSELEFF PIERRE \\
    \hline
    $144$ & KROP ANDRÉ \\
    \hline
    $14$ & LACHAL AIMÉ \\
    \hline
    $173$ & LAMPLE ÉP. LAMPLE HÉLÈNE \\
    \hline
    $42$ & LAUBER MARIANNE \\
    \hline
    $236$ & LAURENT GUILLAUME \\
    \hline
    $122$ & LEBAUD FRÉDÉRIC \\
    \hline
    $104$ & LEBLANC ALAIN \\
    \hline
    $91$ & LE BLANC GUILLAUME \\
    \hline
    $30$ & LE HIR FRANÇOISE \\
    \hline
    $190$ & LEININGER ÉP. CAPDEVIELLE ANNE \\
    \hline
    $61$ & LEMAIRE BERNARD \\
    \hline
    $234$ & LEMAIRE CATHERINE \\
    \hline
    $121$ & LEMBERG HENRI \\
    \hline
    $3$ & LE MERDY CHRISTIAN \\
    \hline
    $135$ & LENTE CHRISTOPHE \\
    \hline
    $195$ & LERAY ÉP. RUELLO MARIANNICK \\
    \hline
    $10$ & LESCOT PAUL \\
    \hline
    $162$ & LESTANG FRANÇOIS \\
    \hline
    $231$ & LETELLIER ANTOINE \\
    \hline
    $193$ & LIGNON JEAN \\
    \hline
    $65$ & LION JEAN \\
    \hline
    $41$ & LODS VÉRONIQUE \\
    \hline
    $141$ & LONGIN GÉRARD \\
    \hline
    $122$ & LOUBIÈRE JOËL \\
    \hline
    $218$ & LOULMET JEAN-CLAUDE \\
    \hline
    $52$ & LUSSIER FRANÇOIS \\
    \hline
    $162$ & LYX JEAN \\
    \hline
    $33$ & MADEC GWENOLA \\
    \hline
    $74$ & MAGNARD DANIELLE \\
    \hline
    $25$ & MAINARD NATHALIE \\
    \hline
    $186$ & MALLEJAC MICHEL \\
    \hline
    $47$ & MALLET CHANTAL \\
    \hline
    $54$ & MALTEY FRANÇOIS \\
    \hline
    $1$ & MANIVEL LAURENT \\
    \hline
    $142$ & MARCON ERIC-PIERRE \\
    \hline
    $104$ & MEGRET PHILIPPE \\
    \hline
    $24$ & MEGUERDITCHIAN IVAN \\
    \hline
    $195$ & MEIGNEN PIERRICK \\
    \hline
    $11$ & MERCIER ÉP. MERCIER NATHALIE \\
    \hline
    $208$ & MERIDA RICARDO \\
    \hline
    $97$ & MIALHE PATRICE \\
    \hline
    $157$ & MICHEL PHILIPPE \\
    \hline
    $175$ & MOTHES HERVÉ \\
    \hline
    $81$ & MOURGUES MARIE \\
    \hline
    $27$ & MOURRAIN BERNARD \\
    \hline
    $54$ & NARDIN BRUNO \\
    \hline
    $165$ & OLIVIER YVES \\
    \hline
    $29$ & PABION PIERRE \\
    \hline
    $84$ & PAILLAS NATHALIE \\
    \hline
    $122$ & PAMPHILE MAX \\
    \hline
    $145$ & PAOLI JEAN \\
    \hline
    $117$ & PARIS JACQUES \\
    \hline
    $108$ & PAUGAM ÉP. MOISY HÉLÈNE \\
    \hline
    $157$ & PENIN JEAN \\
    \hline
    $91$ & PERQUEME MARIE \\
    \hline
    $73$ & PIQUE SERGE \\
    \hline
    $52$ & POURSAT MARIE \\
    \hline
    $101$ & PRADEL MICHEL \\
    \hline
    $178$ & PRECHAC CHRISTOPHE \\
    \hline
    $218$ & PROSPERI SERGE \\
    \hline
    $181$ & QUENOT BERNARD \\
    \hline
    $5$ & RAUCH PATRICK \\
    \hline
    $20$ & REAL CHRISTOPHE \\
    \hline
    $218$ & REINMANN ÉP. PARISOT ANNE \\
    \hline
    $120$ & REY JÉRÔME \\
    \hline
    $178$ & RIVOLLET ALAIN \\
    \hline
    $145$ & ROBY ÉP. ESTAY FLORENCE \\
    \hline
    $84$ & ROCHERON ANNE \\
    \hline
    $94$ & RODARY JACQUES \\
    \hline
    $138$ & ROLLAND HERVÉ \\
    \hline
    $95$ & ROMMEVAUX ÉP. KOELBLEN SABINE \\
    \hline
    $113$ & ROSIERE CAROLE \\
    \hline
    $70$ & ROUQUES JEAN \\
    \hline
    $152$ & ROZIÈRE PAUL \\
    \hline
    $106$ & RUEL PHILIPPE \\
    \hline
    $115$ & SABOURIN HERVÉ \\
    \hline
    $157$ & SANDT ÉP. COLLIGNON GILDA \\
    \hline
    $70$ & SANTONI CLAIRE \\
    \hline
    $97$ & SARLAT JEAN-MICHEL \\
    \hline
    $208$ & SAUNIER ANDRÉ \\
    \hline
    $58$ & SAUNOIS PHILIPPE \\
    \hline
    $1$ & SAUVAGEOT FRANÇOIS \\
    \hline
    $138$ & SCHMITT ÉP. SCHMITT-NICOLAS MARIE \\
    \hline
    $54$ & SDIKA LUC \\
    \hline
    $75$ & SEMINEL ÉP. SCHMITT NATHALIE \\
    \hline
    $162$ & SIBERT GÉRARD \\
    \hline
    $33$ & SIMON MONIQUE \\
    \hline
    $135$ & SIMPELAERE DOMINIQUE \\
    \hline
    $28$ & SOULIER PHILIPPE \\
    \hline
    $208$ & SPAGNOL JEAN-PIERRE \\
    \hline
    $97$ & SQUARCINI CHRISTIAN \\
    \hline
    $138$ & STAMBUL PIERRE \\
    \hline
    $47$ & STANISIC SOPHIE \\
    \hline
    $168$ & THEON PIERRE \\
    \hline
    $218$ & TRICHET CHRISTINE \\
    \hline
    $190$ & TRISTANT JÉRÔME \\
    \hline
    $199$ & TRUONG-HUU PIERRE \\
    \hline
    $233$ & TUDESQ CHRISTIAN \\
    \hline
    $218$ & TULASNE BRIGITTE \\
    \hline
    $108$ & TURNER JACQUES \\
    \hline
    $42$ & TURQUOIS FLORENCE \\
    \hline
    $170$ & VALLERY FRÉDÉRIC \\
    \hline
    $79$ & VALTY JÉRÔME \\
    \hline
    $9$ & VANNIER JEAN \\
    \hline
    $175$ & VAUCANSON ÉP. ROUSSET FRANÇOISE \\
    \hline
    $45$ & VEUILLEZ PIERRE \\
    \hline
    $35$ & VIGNERON CHRISTINE \\
    \hline
    $86$ & VILLARD ANNE \\
    \hline
    $218$ & VINAY MAUD \\
    \hline
    $232$ & WAYMEL BERNARD 232 \\
    \hline
    $218$ & WEIL DOMINIQUE \\
    \hline
    $95$ & WIRTH JEAN \\
    \hline
    $157$ & WIRTZ BRUNO \\
    \hline
    $202$ & YETERIAN GUY \\
    \hline
    $157$ & ZANNI ROGER \\
    \hline
    $149$ & ZANOS JEAN \\
    \hline
  \end{xltabular}

  \begin{flushright}
    {\tiny Source : \url{http://nicolas.martin.ens.free.fr/agreg/1987.html}}
  \end{flushright}
  %</content>
\end{document}
