\input{../common}
\input{../bibliography}

\begin{document}
  %<*content>
  \ranking{1988}

  $299$ admis pour cette session.

  \begin{xltabular}{\linewidth}{|l|X|}
    \hline
    \textbf{Rang} & \textbf{Candidat} \\
    \hline
    $168$ & ABGRALL PHILIPPE \\
    \hline
    $263$ & ABOURJAILY CHAOUKI \\
    \hline
    $115$ & ABRAMOVICI GILLES \\
    \hline
    $191$ & AIX ÉPOUSE PIZETTE MARIE-FRANÇOISE \\
    \hline
    $263$ & AKNIN MYRIAM \\
    \hline
    $68$ & ALBERT LUC \\
    \hline
    $234$ & ALFONSI ADELINE \\
    \hline
    $93$ & ALOUGES FRANÇOIS \\
    \hline
    $86$ & ANSEL JEAN-PASCAL \\
    \hline
    $43$ & ARNAUDON MARC \\
    \hline
    $148$ & ARNOULT JÉRÔME \\
    \hline
    $48$ & ARRIGONI MAURICE \\
    \hline
    $182$ & ATHANAZE GUY \\
    \hline
    $250$ & AUERHAN JEAN \\
    \hline
    $74$ & AUGOT DANIEL \\
    \hline
    $89$ & AURISSERGUES ERIC \\
    \hline
    $176$ & AYOUL BERNARD \\
    \hline
    $214$ & BACHE JEAN-FRANÇOIS \\
    \hline
    $247$ & BAILBÉ CHRISTIAN \\
    \hline
    $110$ & BARBOLOSI DOMINIQUE \\
    \hline
    $113$ & BARITEAU CHRISTINE \\
    \hline
    $263$ & BARONET CLAUDINE \\
    \hline
    $263$ & BAUDRAND GABRIEL \\
    \hline
    $38$ & BELLEBOUCHE DANIEL \\
    \hline
    $206$ & BELLET CLAUDE \\
    \hline
    $165$ & BELLIDO ANNE \\
    \hline
    $16$ & BELLIER ANNELISE \\
    \hline
    $263$ & BELLONI PIERRETTE \\
    \hline
    $263$ & BÉNAT GUY \\
    \hline
    $49$ & BERGER PIERRE \\
    \hline
    $170$ & BÉZOL CLAUDINE \\
    \hline
    $210$ & BIELICZKY PETER \\
    \hline
    $2$ & BIQUARD OLIVIER \\
    \hline
    $234$ & BLANC HENRI \\
    \hline
    $105$ & BLANC ÉPOUSE BACHAS ANNE-MARIE \\
    \hline
    $62$ & BLASCO LAURE \\
    \hline
    $6$ & BOLLE PHILIPPE \\
    \hline
    $46$ & BORRAS CLAUDE \\
    \hline
    $89$ & BOUQUARD JEAN-LOUIS \\
    \hline
    $263$ & BOURGOUIN BRIGITTE \\
    \hline
    $263$ & BOURQUIN RENÉ \\
    \hline
    $40$ & BOUTTELOUP ANNE \\
    \hline
    $79$ & BOUVEROT OLIVIER \\
    \hline
    $201$ & BRIDOUX SYLVIE \\
    \hline
    $156$ & BRIN GEORGES \\
    \hline
    $110$ & BROGLIO ANNIE \\
    \hline
    $119$ & BROUILLARD CHRISTOPHE \\
    \hline
    $136$ & BRUN VINCENT \\
    \hline
    $242$ & BRUNNER GILLES \\
    \hline
    $72$ & BUISSON MICHEL \\
    \hline
    $186$ & BURY JOSÉ \\
    \hline
    $214$ & CABANIAL JEAN-MARC \\
    \hline
    $47$ & CALVI JEAN-PAUL \\
    \hline
    $227$ & CAROFF NATHALIE \\
    \hline
    $43$ & CASTILLON JEAN \\
    \hline
    $130$ & CAVALLO MARC \\
    \hline
    $143$ & CELLIER JACQUES \\
    \hline
    $151$ & CHAMAK MICHEL \\
    \hline
    $234$ & CHAMPROUX ÉPOUSE CLOUET FRANCINE \\
    \hline
    $161$ & CHARPENTIER-TIT FIRMIN \\
    \hline
    $147$ & CHARRIER JEAN-MARC \\
    \hline
    $263$ & CHICHE MICHEL \\
    \hline
    $201$ & CHOLLE ÉPOUSE QUIQUAND SOPHIE \\
    \hline
    $263$ & CHRISTIANY DANIEL \\
    \hline
    $26$ & CIOLFI BRUNO \\
    \hline
    $186$ & CLERC FRÉDÉRIC \\
    \hline
    $250$ & CONSEIL MARIE-LAURE \\
    \hline
    $133$ & CONTRI DANIEL \\
    \hline
    $45$ & COUTENS RÉMI \\
    \hline
    $103$ & DARTYGE CLAIRE \\
    \hline
    $119$ & DASSONVAL CATHY \\
    \hline
    $247$ & DAUJEAN VALÉRIE \\
    \hline
    $182$ & DEBATS ÉPOUSE COGGIA ODILE \\
    \hline
    $124$ & DECKER ÉPOUSE LAMY SYLVIE \\
    \hline
    $153$ & DEFRENNE HUGUES \\
    \hline
    $51$ & DELABAÈRE ERIC \\
    \hline
    $35$ & DELAY BENJAMIN \\
    \hline
    $94$ & DELYON ÉPOUSE BRANDIÈRE ODILE \\
    \hline
    $119$ & DESSE MARIE-LOUISE \\
    \hline
    $170$ & DEVODDÈRE JACQUES \\
    \hline
    $10$ & DEWISME ALAIN \\
    \hline
    $227$ & D'HESMIVY D'AUR JEAN \\
    \hline
    $196$ & DIBLING PATRICE \\
    \hline
    $150$ & DJAOUI ALBERT \\
    \hline
    $234$ & DRESSAYRE ÉPOUSE NOURIGAT MICHELLE \\
    \hline
    $176$ & DUBOUIL JOËL \\
    \hline
    $247$ & DUBOULOZ GEORGES \\
    \hline
    $124$ & DUCASSE ERIC \\
    \hline
    $182$ & DUCEL YVES \\
    \hline
    $118$ & DUPONT GHISLAIN \\
    \hline
    $105$ & DUPONT ÉP. BURET GHISLAINE \\
    \hline
    $214$ & DURAND JEAN-MARIE \\
    \hline
    $263$ & DURTHALLER ÉP. VUILLET COLETTE \\
    \hline
    $210$ & ECKERT CHRISTIAN \\
    \hline
    $148$ & EDOUARD ANTOINE \\
    \hline
    $9$ & EICHENLAUB YVES \\
    \hline
    $176$ & ETHIEVANT ÉP. LEGLANTIER ANNICK \\
    \hline
    $250$ & FELIX GEORGES \\
    \hline
    $77$ & FELLONEAU CLAUDE \\
    \hline
    $142$ & FELTZ ROLAND \\
    \hline
    $148$ & FERRAND JEAN \\
    \hline
    $143$ & FINCK DENIS \\
    \hline
    $242$ & FLAHAUT SERGE \\
    \hline
    $134$ & FLORENT MICHEL \\
    \hline
    $214$ & FLORES FRANÇOIS \\
    \hline
    $151$ & FONTAINE EMMANUEL \\
    \hline
    $54$ & FORTIN NATHALIE \\
    \hline
    $170$ & FOUGERONT JACQUES \\
    \hline
    $263$ & FOURNIER MARIE \\
    \hline
    $86$ & FRADIN PATRICK \\
    \hline
    $143$ & FRANÇOIS JOËL \\
    \hline
    $128$ & FRANSES JEAN-MICHEL \\
    \hline
    $156$ & FRESSON ÉP. TANKERE MARIE \\
    \hline
    $201$ & FRONTISI JULIEN \\
    \hline
    $130$ & FUMEY ALAIN \\
    \hline
    $257$ & GACOGNE LOUIS \\
    \hline
    $180$ & GAMBLIN PASCAL \\
    \hline
    $191$ & GAMBU CHRISTIAN \\
    \hline
    $128$ & GARNIER ÉP. BRAMOULLE LAURENCE \\
    \hline
    $263$ & GAUTHIER FRÉDÉRIC \\
    \hline
    $156$ & GEORGES MAURICE \\
    \hline
    $263$ & GERMANANGUE ANNE \\
    \hline
    $69$ & GIRAUD XAVIER \\
    \hline
    $37$ & GOSSE GÉRARD \\
    \hline
    $176$ & GOTTIN ÉP. \\
    \hline
    $5$ & GOUBET OLIVIER \\
    \hline
    $263$ & GOUMI MICHEL \\
    \hline
    $23$ & GOURNAY LAURENT \\
    \hline
    $260$ & GRAC NATHALIE \\
    \hline
    $40$ & GRÉBERT BENOIT \\
    \hline
    $100$ & GRUNER ILME \\
    \hline
    $104$ & GUÉRINEAU ÉP. BOURNAUD MIREILLE \\
    \hline
    $227$ & GUILLAUD ALAIN \\
    \hline
    $119$ & GUILLERMARD CHRISTOPHE \\
    \hline
    $88$ & GUILLOT PHILIPPE \\
    \hline
    $210$ & GUINTRAND ÉP. DUQUENNOY JACQUELINE \\
    \hline
    $130$ & HALLER DOMINIQUE \\
    \hline
    $170$ & HAMEL THIERRY \\
    \hline
    $214$ & HARDOUIN JEAN \\
    \hline
    $168$ & HARIRI MUSTAPHA \\
    \hline
    $263$ & HEINTZMANN MICHEL \\
    \hline
    $263$ & HURAULT JEAN-MICHEL \\
    \hline
    $186$ & JACAMON ÉP. SALVO ANNE \\
    \hline
    $201$ & JARRY MURIELLE \\
    \hline
    $206$ & JASKOLSKI ERIC \\
    \hline
    $260$ & JOINT MARIE \\
    \hline
    $161$ & JOSSET-LAMAUGAR HÉLÈNE \\
    \hline
    $95$ & JOUVE FRANÇOIS \\
    \hline
    $170$ & JOYEUX ÉP. GRÉSIL SYLVIE \\
    \hline
    $186$ & KERVADEC ELISABETH \\
    \hline
    $186$ & KIENTZ ALAIN \\
    \hline
    $19$ & KLOPP FRÉDÉRIC \\
    \hline
    $196$ & KUZNIAK ALAIN \\
    \hline
    $81$ & LACAILLE JÉRÔME \\
    \hline
    $72$ & LACOUTURE CLAUDE \\
    \hline
    $1$ & LAFFORGUE LAURENT \\
    \hline
    $124$ & LAHANIER ÉP. CAIGNAERT DOMINIQUE \\
    \hline
    $260$ & LALITTE CHRISTIAN \\
    \hline
    $136$ & LALLEMENT HUBERT \\
    \hline
    $250$ & LAMARQUE CLAUDE \\
    \hline
    $57$ & LAMY OLIVIER \\
    \hline
    $23$ & LANDART ANTOINE \\
    \hline
    $263$ & LATERZA RENÉ \\
    \hline
    $105$ & LAURENS CLAUDINE \\
    \hline
    $7$ & LAURENS JÉRÔME \\
    \hline
    $59$ & LAVAL FRÉDÉRIC \\
    \hline
    $191$ & LAVERGNE ÉP. ISLER DOMINIQUE \\
    \hline
    $153$ & LE BAIL DENIS \\
    \hline
    $139$ & LEBAUD MARIE-PIERRE \\
    \hline
    $81$ & LE BIHAN ANNE \\
    \hline
    $54$ & LECLERC RAYMOND \\
    \hline
    $196$ & LECOMTE DOMINIQUE \\
    \hline
    $66$ & LECUYER FRANCIS \\
    \hline
    $263$ & LEDOUX LAURENCE \\
    \hline
    $17$ & LE GALL PASCALE \\
    \hline
    $105$ & LE GALL POL \\
    \hline
    $17$ & LÉGER DENIS \\
    \hline
    $14$ & LE GLUHER JEAN \\
    \hline
    $214$ & LEGUESDRON ABDELLYJEAN \\
    \hline
    $234$ & LELOUREC HERVÉ \\
    \hline
    $51$ & LE QUINTREC ISABELLE \\
    \hline
    $59$ & LERBET JEAN \\
    \hline
    $40$ & LEROUX PHILIPPE \\
    \hline
    $78$ & LEROY MARTIAL \\
    \hline
    $165$ & LESAGE ISABELLE \\
    \hline
    $10$ & LESCOP CHRISTINE \\
    \hline
    $124$ & LESCURE FRANÇOISE \\
    \hline
    $74$ & LIGIER RENÉ \\
    \hline
    $180$ & LIMARE ARMELLE \\
    \hline
    $234$ & LION MICHEL \\
    \hline
    $98$ & LITOVSKY IGOR \\
    \hline
    $153$ & LOCHE CAROLINE \\
    \hline
    $156$ & LOFREDI PIERRE \\
    \hline
    $3$ & LOGAK ELISABETH \\
    \hline
    $242$ & LOUISET ROBERT \\
    \hline
    $99$ & LUCAS EDOUARD \\
    \hline
    $250$ & LUCIEN CALLEAU RENÉ \\
    \hline
    $115$ & MAILLARD CHRISTIAN \\
    \hline
    $57$ & MAINET VÉRONIQUE \\
    \hline
    $191$ & MAKIL XAVIER \\
    \hline
    $66$ & MAMET ÉP. DE JONGHE PASCALE \\
    \hline
    $21$ & MANCUSO FRÉDÉRIC \\
    \hline
    $10$ & MARCHE CLAUDE \\
    \hline
    $100$ & MARI PIERRE \\
    \hline
    $224$ & MARIANELLI ÉP. OZENDA ODILE \\
    \hline
    $257$ & MARIE ÉP. FONTANIER PATRICIA \\
    \hline
    $27$ & MARTINEZ ISABELLE \\
    \hline
    $242$ & MASSON ÉP. ROLLAND CLAUDIE \\
    \hline
    $263$ & MAYER ANNE \\
    \hline
    $263$ & MEGARBANE NAIM \\
    \hline
    $227$ & MERCERON SERGE \\
    \hline
    $28$ & MERLE ERIC \\
    \hline
    $14$ & MEYRE THIERRY \\
    \hline
    $263$ & MICHOUD CLAIRE \\
    \hline
    $38$ & MICLO LAURENT \\
    \hline
    & MIDELTON MARIE \\
    \hline
    $234$ & MOLINIER PHILIPPE \\
    \hline
    $263$ & MORILLON JEAN-PAUL \\
    \hline
    $49$ & MOUTON FRÉDÉRIC \\
    \hline
    $263$ & MOUTTON MIREILLE \\
    \hline
    $168$ & NÈGRE CHRISTIAN \\
    \hline
    $89$ & NIASS IBRAHIMA \\
    \hline
    $214$ & NICOLEAU FRANÇOIS \\
    \hline
    $227$ & NIEDERMAN LAURENT \\
    \hline
    $250$ & OBRIST ROBERT \\
    \hline
    $139$ & OLIVIER JEAN \\
    \hline
    $214$ & ORTIZ PASCAL \\
    \hline
    $139$ & PACULL CHRISTIAN \\
    \hline
    $95$ & PALISSE RENAUD \\
    \hline
    $263$ & PALOMARES PATRICK \\
    \hline
    $69$ & PANSE NICOLE \\
    \hline
    $13$ & PARISSE BERNARD \\
    \hline
    $33$ & PASCAL FRÉDÉRIC \\
    \hline
    $156$ & PASQUIER PHILIPPE \\
    \hline
    $263$ & PEREZ LYDIE \\
    \hline
    $59$ & PERRAULT CATHERINE \\
    \hline
    $161$ & PETIT PASCALE \\
    \hline
    $195$ & PETITOT GÉRARD \\
    \hline
    $201$ & PHILIPPE FABRICE \\
    \hline
    $79$ & PICAUD JEAN \\
    \hline
    $227$ & PONCET MICHEL \\
    \hline
    $105$ & PONCY MICHEL \\
    \hline
    $263$ & POULAIN DENIS \\
    \hline
    $62$ & PRÉVOST THIERRY \\
    \hline
    $84$ & QUENEZ MARIE \\
    \hline
    $115$ & RAGEUL ÉP. PETITJEAN PATRICIA \\
    \hline
    $8$ & RAMARE OLIVIER \\
    \hline
    $182$ & RAMOND THIERRY \\
    \hline
    $263$ & RAYNARD JEAN \\
    \hline
    $234$ & RAYNAUD DE FITT PAUL \\
    \hline
    $196$ & RECH PIERRE \\
    \hline
    $119$ & REGNARD IDELETTE \\
    \hline
    $84$ & RIBAUT FRANCINE \\
    \hline
    $91$ & RIBON OLIVIER \\
    \hline
    $161$ & ROBBES DIDIER \\
    \hline
    $74$ & ROBLET EMMANUEL \\
    \hline
    $113$ & ROCTON PATRICK \\
    \hline
    $224$ & ROGEZ BERNARD \\
    \hline
    $65$ & ROSSELLE ÉP. BERGONZINI MARIE \\
    \hline
    $257$ & ROSSIGNOL STÉPHANE \\
    \hline
    $81$ & ROUSSILLON ROLAND \\
    \hline
    $263$ & ROUSSY FRÉDÉRIQUE \\
    \hline
    $31$ & ROY LAURENT \\
    \hline
    $210$ & SABATIER ÉP. JACQUE FRANÇOISE \\
    \hline
    $91$ & SABY NICOLAS \\
    \hline
    $90$ & SACRE CHRISTINE \\
    \hline
    $263$ & SAINT-PIERRE GÉRARD \\
    \hline
    $206$ & SARFATI JEAN \\
    \hline
    $143$ & SAUX PHILIPPE \\
    \hline
    $36$ & SAUZIN DAVID \\
    \hline
    $62$ & SCHMITT JEAN \\
    \hline
    $263$ & SCHMITT ÉP. LAABID FRANCINE \\
    \hline
    $25$ & SCHNEPF FRANÇOIS \\
    \hline
    $170$ & SCHOOTER ÉPOUSE LITOVSKY ANNE-MARIE \\
    \hline
    $263$ & SERT ALAIN \\
    \hline
    $263$ & SHIH JIZHUANG \\
    \hline
    $28$ & SMIETANSKI FRÉDÉRIC \\
    \hline
    $19$ & SOUCARIS ARNAUD \\
    \hline
    $54$ & SOYEUR ALAIN \\
    \hline
    $53$ & STENGEL FRANK \\
    \hline
    $97$ & STROHL ÉPOUSE LEFEBVRE MARIE \\
    \hline
    $214$ & SUBTIL ERIC \\
    \hline
    $263$ & SYLVAIN MARC \\
    \hline
    $102$ & THIENARD JEAN \\
    \hline
    $69$ & TORDO-ROMBAUT IRÈNE \\
    \hline
    $21$ & TROUVE ALAIN \\
    \hline
    $32$ & ULLMO EMMANUEL \\
    \hline
    $214$ & VALORY FRÉDÉRIC \\
    \hline
    $34$ & VASSEROT ERIC \\
    \hline
    $134$ & VAUGIRARD VICTOR \\
    \hline
    $165$ & VESCHAMBRE PHILIPPE \\
    \hline
    $206$ & VINDOT CORINNE \\
    \hline
    $136$ & VITTEL REBÉ \\
    \hline
    $3$ & VIX CHARLES \\
    \hline
    $224$ & WEISS MICHÈLE \\
    \hline
    $227$ & WILL EMMANUEL \\
    \hline
    $196$ & WOLF MARIE-FRANÇOISE \\
    \hline
    $110$ & XUEREB THIERRY \\
    \hline
    $242$ & ZILIOTTO CLÉMENT \\
    \hline
  \end{xltabular}

  \begin{flushright}
    {\tiny Source : \url{http://nicolas.martin.ens.free.fr/agreg/1988.html}}
  \end{flushright}
  %</content>
\end{document}
