\input{../common}
\input{../bibliography}

\begin{document}
  %<*content>
  \ranking{1989}

  $354$ admis pour cette session.

  \begin{xltabular}{\linewidth}{|l|X|}
    \hline
    \textbf{Rang} & \textbf{Candidat} \\
    \hline
    $84$ & ADELON ALFRED \\
    \hline
    $217$ & ADJAMAGBO KOSSIVI \\
    \hline
    $317$ & ADOLLE ROBERT \\
    \hline
    $201$ & ALLIOT MURIEL \\
    \hline
    $88$ & ALLUCHON ANDRÉ \\
    \hline
    $178$ & ANDRÉ JEAN \\
    \hline
    $212$ & ARNOULT STÉPHANE \\
    \hline
    $64$ & ASTRUC THIERRY \\
    \hline
    $65$ & AUBOURG ERIC \\
    \hline
    $317$ & AZZOUZI EL MOKHTAR \\
    \hline
    $65$ & BACHE JEAN \\
    \hline
    $121$ & BALVAY PIERRE \\
    \hline
    $289$ & BANTIGNY JEZEQUEL CHRISTINE \\
    \hline
    $289$ & BARIL PATRICK \\
    \hline
    $172$ & BARKATS DIDIER \\
    \hline
    $172$ & BARKATS DIDIER \\
    \hline
    $264$ & BARKATS FRÉDÉRIQUE \\
    \hline
    $276$ & BARY CLAUDE \\
    \hline
    $197$ & BASSE MARTINE \\
    \hline
    $121$ & BAUDRIMONT PASCAL \\
    \hline
    $237$ & BAUMANN ÉP. BAUMANN ODILE \\
    \hline
    $313$ & BAUS ÉP. CALCINE NOELLE \\
    \hline
    $136$ & BAVENCOFFE EDGARD \\
    \hline
    $162$ & BELGACEM MONGI \\
    \hline
    $183$ & BELLIARD ROSELYNE \\
    \hline
    $201$ & BELOUAZZA ÉP. TAUZIN RACHIDA \\
    \hline
    $108$ & BENETTI FRANÇOIS \\
    \hline
    $163$ & BENHAYOUN PAUL \\
    \hline
    $51$ & BERGER ÉP. GROS PASCALE \\
    \hline
    $317$ & BERNARD ÉP. LONGIN GABRIELLE \\
    \hline
    $270$ & BERNARD ÉP. POMBOURCQ PASCALE \\
    \hline
    $30$ & BERNE CORINNE \\
    \hline
    $81$ & BESBES MOURAD \\
    \hline
    $151$ & BILLON ÉP. LEFEVRE ANNE \\
    \hline
    $96$ & BILLUART JEAN \\
    \hline
    $96$ & BIROT ÉP. DE LABACHELERIE FRANÇOISE \\
    \hline
    $317$ & BLANC VÉRONIQUE \\
    \hline
    $297$ & BLANDIER DANIEL \\
    \hline
    $258$ & BOGIRAUD CHRISTINE \\
    \hline
    $264$ & BONJOUR CHRISTOPHE \\
    \hline
    $317$ & BONNARD FRÉDÉRIC \\
    \hline
    $81$ & BONNEAU GEORGES-PIERRE \\
    \hline
    $163$ & BOUCHET BRIGITTE \\
    \hline
    $191$ & BOUCHET ÉP. BENETEAU FLORENCE \\
    \hline
    $21$ & BOUCHUT FRANÇOIS \\
    \hline
    $217$ & BOUILLERET ALETH \\
    \hline
    $81$ & BOULADOUX FRANÇOIS \\
    \hline
    $96$ & BOURGUIN PHILIPPE \\
    \hline
    $1$ & BOUSQUET-MELOU MIREILLE \\
    \hline
    $317$ & BOUTON GILLES \\
    \hline
    $306$ & BOVANI MICHEL \\
    \hline
    $214$ & BOYER GERMAIN \\
    \hline
    $317$ & BOYEZ SERGE \\
    \hline
    $264$ & BRAULT ROGER \\
    \hline
    $217$ & BRESTOVSKI MICHEL \\
    \hline
    $188$ & BREUVART ALAIN \\
    \hline
    $13$ & BRIEZ DOMINIQUE \\
    \hline
    $297$ & BRISSAUD MICHEL \\
    \hline
    $27$ & BROCHET DANIELLE \\
    \hline
    $78$ & BROUCQUART ÉP. GUÉRIN ANNE-MARIE \\
    \hline
    $32$ & BRUNETON LOIC \\
    \hline
    $2$ & BURQ NICOLAS \\
    \hline
    $270$ & CAMILLE VIRGINIE \\
    \hline
    $19$ & CARDALIAGUET PIERRE \\
    \hline
    $286$ & CARON MICHEL \\
    \hline
    $276$ & CARPAYE JEAN \\
    \hline
    $183$ & CAUCHOIS PAUL-EMILE \\
    \hline
    $237$ & CAZANAVE-NEBOUT ÉP. CAZANAVE-NEBOUT NICOLE \\
    \hline
    $261$ & CAZAUX MURIEL \\
    \hline
    $9$ & CHAMBOLLE ANTONIN \\
    \hline
    $303$ & CHANET ROGER \\
    \hline
    $93$ & CHEVET GÉRARD \\
    \hline
    $84$ & CHICOURRAT MONIQUE \\
    \hline
    $197$ & COFFINIER JEAN-MICHEL \\
    \hline
    $21$ & COLLIN PASCAL \\
    \hline
    $48$ & COMBES BERNARD \\
    \hline
    $317$ & COQUIL CATHERINE \\
    \hline
    $6$ & CORREIA HUBERT \\
    \hline
    $306$ & CORTADO FRANCIS \\
    \hline
    $78$ & CORTELLA ANNE \\
    \hline
    $4$ & COULET CYRILLE \\
    \hline
    $270$ & COUTU BERNARD \\
    \hline
    $77$ & CREGUT PIERRE \\
    \hline
    $44$ & CREIGNOU NADIA \\
    \hline
    $224$ & CREMERS HUBERT \\
    \hline
    $264$ & DAILLY PAUL \\
    \hline
    $221$ & DEBOCK JEAN-LOUIS \\
    \hline
    $13$ & DE BOUARD ANNE \\
    \hline
    $310$ & DE BURGHGRAEVE FRANÇOIS \\
    \hline
    $317$ & DECAMPS JEAN-PAUL \\
    \hline
    $276$ & DE CHARLES NICOLAS \\
    \hline
    $40$ & DECREUSEFOND LAURENT \\
    \hline
    $43$ & DEGORCE ERIC \\
    \hline
    $75$ & DELBOS DANIEL \\
    \hline
    $160$ & DELECRIN JOËL \\
    \hline
    $191$ & DELIAN ARNAUD \\
    \hline
    $136$ & DEMANGE DANIEL \\
    \hline
    $317$ & DENIER JEAN-PIERRE \\
    \hline
    $243$ & DEPAUW JÉRÔME \\
    \hline
    $30$ & DEVULDER CHRISTOPHE \\
    \hline
    $153$ & DUA DENIS \\
    \hline
    $276$ & DUBOST HENRI \\
    \hline
    $243$ & DUCROZ PATRICE \\
    \hline
    $131$ & DUFLOS ÉP. WEILL CHRISTINE \\
    \hline
    $253$ & DULAC PHILIPPE \\
    \hline
    $317$ & DUPERRET JEAN \\
    \hline
    $96$ & DUPONT-YACAUD PIERRE \\
    \hline
    $270$ & DUPRÉ JEAN-MARIE \\
    \hline
    $35$ & DURAND CLAUDE \\
    \hline
    $297$ & DURCZEWSKI HENRI-PAUL \\
    \hline
    $303$ & DUSSART BENOIT \\
    \hline
    $204$ & EL ABDI ABDELILAH \\
    \hline
    $313$ & EL BAZ BENSION \\
    \hline
    $232$ & ELHRAICHI JAMAL \\
    \hline
    $297$ & EVENO JEAN-LUC \\
    \hline
    $276$ & FAULON RÉMY \\
    \hline
    $108$ & FAUVET ÉP. BATHIER MICHÈLE \\
    \hline
    $13$ & FAVENNEC DENIS \\
    \hline
    $88$ & FELLAH DOMINIQUE \\
    \hline
    $276$ & FETIVEAU RAYMOND \\
    \hline
    $119$ & FLORI CHRISTOPHE \\
    \hline
    $52$ & FONTAINE PHILIPPE \\
    \hline
    $317$ & FOSSATI NICOLAS \\
    \hline
    $37$ & FOUBERT LAURENT \\
    \hline
    $163$ & FOURCADE ERIC \\
    \hline
    $317$ & FOURNIER JEAN-DENIS \\
    \hline
    $80$ & FRANCHINO YVES \\
    \hline
    $224$ & FRANCON NADINE \\
    \hline
    $183$ & FRICKER DANIÈLE \\
    \hline
    $178$ & FRIEDERICH PIERRE \\
    \hline
    $306$ & GABILLARD ÉP. RIBAS SYLVETTE \\
    \hline
    $46$ & GABORIAU DAMIEN \\
    \hline
    $228$ & GAC PHILIPPE \\
    \hline
    $114$ & GALLOIS MIRENTCHU \\
    \hline
    $121$ & GARCIA JÉSUS \\
    \hline
    $188$ & GARÇON GABRIEL \\
    \hline
    $253$ & GARNIER JEAN-MARC \\
    \hline
    $62$ & GAUTHERON PHILIPPE \\
    \hline
    $8$ & GAVAGE SYLVIE \\
    \hline
    $191$ & GEGOUT ANNE \\
    \hline
    $60$ & GENESTIER ALAIN \\
    \hline
    $286$ & GEOFFARD PIERRE-YVES \\
    \hline
    $101$ & GERBIER SYLVIE \\
    \hline
    $264$ & GILARDI JEAN \\
    \hline
    $147$ & GILLES JOSÉ \\
    \hline
    $160$ & GINGREAU ISABELLE \\
    \hline
    $243$ & GIOVACHINI SOPHIE \\
    \hline
    $172$ & GIRAUD PIERRE \\
    \hline
    $93$ & GIRAULT ÉP. ADJADJ ANNICK \\
    \hline
    $112$ & GIVORD CHRISTOPHE \\
    \hline
    $134$ & GOICHOT FRANÇOIS \\
    \hline
    $317$ & GOUALARD JEAN \\
    \hline
    $191$ & GOURGOUDOU AMADOU \\
    \hline
    $38$ & GOURGOULHON ERIC \\
    \hline
    $134$ & GOURMELEN ÉP. MERDY MARYVONNE \\
    \hline
    $183$ & GRANDCOLAS MICHEL \\
    \hline
    $163$ & GRIMAL JEAN-PIERRE \\
    \hline
    $317$ & GRISONI PASCAL \\
    \hline
    $276$ & GROISON JEAN-MARC \\
    \hline
    $63$ & GUELFI PASCAL \\
    \hline
    $317$ & GUERCHAIS CHRISTOPHE \\
    \hline
    $237$ & GUERRY GRAZIELLA \\
    \hline
    $306$ & GUEZENNEC JACQUES \\
    \hline
    $317$ & GUILLAUME JEAN \\
    \hline
    $317$ & HAKENHOLZ CHRISTIAN \\
    \hline
    $70$ & HELLAL KARIM \\
    \hline
    $191$ & HELSON PIERRE \\
    \hline
    $243$ & HELSON ÉP. THOLY FRANÇOISE \\
    \hline
    $204$ & HERBELIN HUGO \\
    \hline
    $317$ & HERVÉ MARIE-ANNICK \\
    \hline
    $147$ & HERVEIC BRIGITTE \\
    \hline
    $131$ & HIVET CLAIRE \\
    \hline
    $91$ & HONVAULT PASCAL \\
    \hline
    $158$ & HOUDEMENT CATHERINE \\
    \hline
    $136$ & HOUILLON ISABELLE \\
    \hline
    $178$ & IROIR MICHEL \\
    \hline
    $88$ & JAMET PIERRE-YVES \\
    \hline
    $317$ & JANNIN JEAN-PIERRE \\
    \hline
    $204$ & JARRY JEAN-LOUIS \\
    \hline
    $224$ & JEANNERET CATHERINE \\
    \hline
    $163$ & JEDDARI LARBI \\
    \hline
    $44$ & JEHANNE ARNAUD \\
    \hline
    $276$ & JOSSE ALFRÉDÉRIC \\
    \hline
    $221$ & JOURDAIN ERIC \\
    \hline
    $197$ & JOZWIAK RAYMOND \\
    \hline
    $21$ & KAMMERER CLOTILDE \\
    \hline
    $18$ & KERDELHUE PHILIPPE \\
    \hline
    $93$ & KHATISSIAN CHRISTOPHE \\
    \hline
    $317$ & KLEIN ÉP. CHAMPAGNE BRIGITTE \\
    \hline
    $101$ & KUCZMA FRÉDÉRIC \\
    \hline
    $183$ & LACROIX YVES \\
    \hline
    $221$ & LAFONT JACQUES \\
    \hline
    $129$ & LAINÉ PASCAL \\
    \hline
    $289$ & LALOUM ÉP. TRABBIA MICHÈLE \\
    \hline
    $136$ & LANGEVIN PHILIPPE \\
    \hline
    $286$ & LARUE CHRISTIAN \\
    \hline
    $317$ & LAST CÉCILE \\
    \hline
    $310$ & LATROMPETTE JEAN-MARIE \\
    \hline
    $112$ & LAUNAY JEAN-PIERRE \\
    \hline
    $9$ & LAURENCOT PHILIPPE \\
    \hline
    $73$ & LAURENT BÉATRICE \\
    \hline
    $70$ & LAURENT GUILLAUME \\
    \hline
    $53$ & LAURENT SERGE \\
    \hline
    $207$ & LAVERNY NOËL \\
    \hline
    $261$ & LECOUTURIER JEAN \\
    \hline
    $155$ & LECUYER VINCENT \\
    \hline
    $143$ & LE FOULGOCQ SYLVIE \\
    \hline
    $151$ & LE LAY MARIANIG \\
    \hline
    $47$ & LELIÈVRE HUBERT \\
    \hline
    $154$ & LEMAIRE ÉP. RAYNARD CATHERINE \\
    \hline
    $119$ & LEPANNETIER GÉRARD \\
    \hline
    $228$ & LE PANSE DIDIER \\
    \hline
    $207$ & LE STANG ALAIN \\
    \hline
    $178$ & LETORT PIERRE-YVES \\
    \hline
    $147$ & LEYRIS CLAUDE \\
    \hline
    $243$ & LIZAN-ESQUERRET VÉRONIQUE \\
    \hline
    $191$ & LOGE JEAN-PAUL \\
    \hline
    $61$ & LOPEZ CHRISTIAN \\
    \hline
    $108$ & LOSSENT PIERRE \\
    \hline
    $35$ & LOUIS JEAN-DOMINIQUE \\
    \hline
    $232$ & LOVAT BRUNO \\
    \hline
    $67$ & LUMBROSO PHILIPPE \\
    \hline
    $84$ & MAHIEU CHRISTOPHE \\
    \hline
    $67$ & MALIGE GILLES \\
    \hline
    $197$ & MALLARD PHILIPPE \\
    \hline
    $108$ & MARCOTTE THIERRY \\
    \hline
    $264$ & MARÉCHAL GILLES \\
    \hline
    $258$ & MARQUANT CHRYSTELL \\
    \hline
    $84$ & MARQUE FRANÇOIS \\
    \hline
    $136$ & MARTIANO JEAN-JACQUES \\
    \hline
    $317$ & MAUPU ODILE \\
    \hline
    $54$ & MAURIELLE GÉRARD \\
    \hline
    $232$ & MAZALEYRAT FRANÇOIS \\
    \hline
    $158$ & MEAR PATRICK \\
    \hline
    $204$ & MENETRIEUX BRIGITTE \\
    \hline
    $70$ & MENINI CHANTAL \\
    \hline
    $115$ & MEREL LOIC \\
    \hline
    $147$ & MEYER PATRICIA \\
    \hline
    $48$ & MIALET JEAN-NOËL \\
    \hline
    $26$ & MICHEL VINCENT \\
    \hline
    $237$ & MIGNON PHILIPPE \\
    \hline
    $261$ & MOINARD ÉP. LOUVIN DOMINIQUE \\
    \hline
    $7$ & MONFRONT FABRICE \\
    \hline
    $303$ & MOURRET BERNARD \\
    \hline
    $21$ & NAGOT ISABELLE \\
    \hline
    $128$ & NALIN OLIVIER \\
    \hline
    $104$ & NAPIERACZ MAGALI \\
    \hline
    $91$ & NASSIET FRANCIS \\
    \hline
    $232$ & NICOLAZO-CRACH PAUL \\
    \hline
    $317$ & NICOLLON DES AB BERTRAND \\
    \hline
    $237$ & NOËL PATRICK \\
    \hline
    $228$ & OURIOU MARIE-CHRISTINE \\
    \hline
    $243$ & OZENDA MAX \\
    \hline
    $115$ & PAGÈS HERVÉ \\
    \hline
    $276$ & PAILLARD SERGE \\
    \hline
    $178$ & PAPADOPOULO THÉODORE \\
    \hline
    $243$ & PARFAIT PHILIPPE \\
    \hline
    $207$ & PARIS ALAIN \\
    \hline
    $54$ & PATARIN JACQUES \\
    \hline
    $11$ & PATRAS FRÉDÉRIC \\
    \hline
    $143$ & PAYET WILLY \\
    \hline
    $136$ & PECHOUX PAUL \\
    \hline
    $317$ & PÉPIN ALAIN \\
    \hline
    $170$ & PÉPIN DENIS \\
    \hline
    $276$ & PERNAS LOUIS \\
    \hline
    $228$ & PESSO JEAN \\
    \hline
    $104$ & PETIT PASCAL \\
    \hline
    $3$ & PEYRE EMMANUEL \\
    \hline
    $121$ & PIQUÉE VINCENT \\
    \hline
    $143$ & PITTAVINO MICHEL \\
    \hline
    $317$ & PIZETTE FRANÇOIS \\
    \hline
    $253$ & POURRET PHILIPPE \\
    \hline
    $253$ & POURTIER JEAN \\
    \hline
    $81$ & PRÉAULT JEAN-MARIE \\
    \hline
    $289$ & PRÉVOT ALAIN \\
    \hline
    $317$ & PUECH NICOLAS \\
    \hline
    $317$ & QUEROU NICOLE \\
    \hline
    $317$ & QUEVILLE CHRISTINE \\
    \hline
    $237$ & RALAIVOLA ALAIN \\
    \hline
    $96$ & RANDRIAMASY CHRISTIANE \\
    \hline
    $258$ & RENARD SOPHIE \\
    \hline
    $172$ & RICHARD LAURENT-MARIE \\
    \hline
    $220$ & RINEAU JEAN-PHILIPPE \\
    \hline
    $54$ & RIVAT JOËL \\
    \hline
    $40$ & ROBERT GILLES \\
    \hline
    $73$ & ROBUTEL PHILIPPE \\
    \hline
    $136$ & ROCH ÉP. HUMBERT MARTINE \\
    \hline
    $34$ & ROMON PASCAL \\
    \hline
    $13$ & ROSAZ LAURENT \\
    \hline
    $17$ & ROSIER LIONEL \\
    \hline
    $104$ & ROUSSEL JEAN \\
    \hline
    $129$ & RUMIN MICHEL \\
    \hline
    $224$ & SAINT-LANNES ÉP. COUSTEAU MARYSE \\
    \hline
    $253$ & SAINT-PIERRE FRANÇOIS \\
    \hline
    $289$ & SAINTS-JOURS BERNARD \\
    \hline
    $214$ & SAYERLE SYLVIE \\
    \hline
    $11$ & SERLET LAURENT \\
    \hline
    $40$ & SERNA DIDIER \\
    \hline
    $310$ & SERRE ÉP. RAYNAUD VIVIANE \\
    \hline
    $270$ & SIGWARD ERIC \\
    \hline
    $289$ & SIMON FRÉDÉRIC \\
    \hline
    $75$ & SIROT JEAN-MARIE \\
    \hline
    $101$ & SOLET ISABELLE \\
    \hline
    $107$ & SORBE XAVIER \\
    \hline
    $27$ & SORGIUS ISABELLE \\
    \hline
    $115$ & SOUFFLET PIERRE \\
    \hline
    $289$ & SOULIER LAURENCE \\
    \hline
    $212$ & SOUPLET PHILIPPE \\
    \hline
    $317$ & STAELENS JEAN \\
    \hline
    $48$ & STEF ANDRÉ \\
    \hline
    $126$ & STOLL ANDRÉ \\
    \hline
    $33$ & STRECKER VIOLAINE \\
    \hline
    $121$ & STUSSI DAMARIS \\
    \hline
    $207$ & SUFFRIN FRÉDÉRIC \\
    \hline
    $313$ & SURSIN THIERRY \\
    \hline
    $313$ & TAMIM EL JARKAS FADI \\
    \hline
    $270$ & TASSIN EMMANUEL \\
    \hline
    $54$ & TATISCHEFF SERGE \\
    \hline
    $289$ & THENAULT FRANÇOIS \\
    \hline
    $20$ & THERET JULIEN \\
    \hline
    $214$ & THOMASSIN RÉGINE \\
    \hline
    $207$ & TISSERAND FRANÇOIS \\
    \hline
    $5$ & TOSEL NICOLAS \\
    \hline
    $163$ & TOURY ÉP. GRENIER FRANÇOISE \\
    \hline
    $297$ & TOUYRE LAURENT \\
    \hline
    $131$ & TRANDIT-HAUEUR JEAN-PAUL \\
    \hline
    $126$ & TRETON PATRICE \\
    \hline
    $201$ & TRICOIRE DANIEL \\
    \hline
    $163$ & TRYSTRAM JEAN-CHARLES \\
    \hline
    $143$ & TUDESQ CHRISTIAN \\
    \hline
    $39$ & URBAN ERIC \\
    \hline
    $297$ & VAILLANT MARC-ANDRÉ \\
    \hline
    $21$ & VALLET GUY \\
    \hline
    $172$ & VALLETTA JEAN \\
    \hline
    $155$ & VALMORIN VINCENT \\
    \hline
    $317$ & VANDEWIELL DIDIER \\
    \hline
    $232$ & VASSAL MARIE-NOËLLE \\
    \hline
    $243$ & VASSEUR HERVÉ \\
    \hline
    $217$ & VAUTHIER BERNARD \\
    \hline
    $115$ & VENTACH FABRICE \\
    \hline
    $243$ & VERGNES BRUNO \\
    \hline
    $317$ & VERGULT MICHEL \\
    \hline
    $243$ & VERHAEGHE THIERRY \\
    \hline
    $54$ & VEYSSEYRE PHILIPPE \\
    \hline
    $67$ & VIEILLE NICOLAS \\
    \hline
    $190$ & VIGNAUX PHILIPPE \\
    \hline
    $317$ & VIGNERON RENÉ \\
    \hline
    $170$ & VINAUER GEORGES \\
    \hline
    $54$ & VINCENT LUC \\
    \hline
    $155$ & VINCIGUERRA LUCIEN \\
    \hline
    $172$ & VIPREY ÉP. JACQUIN MARTINE \\
    \hline
    $172$ & WEINSANTO LIONEL \\
    \hline
    $27$ & WERNER WENDELIN \\
    \hline
    $317$ & YAHIATENE AHMED \\
    \hline
  \end{xltabular}

  \begin{flushright}
    {\tiny Source : \url{http://nicolas.martin.ens.free.fr/agreg/1989.html}}
  \end{flushright}
  %</content>
\end{document}
