\input{../common}
\input{../bibliography}

\begin{document}
  %<*content>
  \ranking{1992}

  $422$ admis pour cette session.

  \begin{xltabular}{\linewidth}{|l|X|}
    \hline
    \textbf{Rang} & \textbf{Candidat} \\
    \hline
    $213$ & ABALLEA CHRISTOPHE \\
    \hline
    $216$ & ABOU ISABELLE \\
    \hline
    $400$ & ADJEDJ BRIGITTE \\
    \hline
    $228$ & ADOLLE JEAN-BAPTISTE \\
    \hline
    $258$ & AIRAUD NATHALIE \\
    \hline
    $169$ & ALEXIS FLORIAN \\
    \hline
    $200$ & ALVES DENIS \\
    \hline
    $206$ & AMELOT ÉP. ARROU-VIGNOD MARTINE \\
    \hline
    $367$ & ANTONELLI PHILIPPE \\
    \hline
    $200$ & ANTONETTI RUGGI JEAN \\
    \hline
    $87$ & APPEL WALTER \\
    \hline
    $258$ & ARAGON SERGE \\
    \hline
    $147$ & AUBRY PHILIPPE \\
    \hline
    $339$ & BAIKARI NOUR-EDDINE \\
    \hline
    $155$ & BAILLARGEAU ÉRIC \\
    \hline
    $54$ & BALAVOINE DAVID \\
    \hline
    $360$ & BALEMBITS FABRICE \\
    \hline
    $92$ & BALLAN ARNAUD \\
    \hline
    $128$ & BARALE MAGALI \\
    \hline
    $24$ & BARBAZA LAURENT \\
    \hline
    $255$ & BARBIER VALÉRIE \\
    \hline
    $403$ & BASSILA NABIL \\
    \hline
    $351$ & BASSO PIERRE \\
    \hline
    $200$ & BAUDOUIN NATHALIE \\
    \hline
    $31$ & BAY XAVIER \\
    \hline
    $367$ & BEAULIEU VALÉRIE \\
    \hline
    $87$ & BELABAS KARIM \\
    \hline
    $172$ & BELKILANI ABDELKADER \\
    \hline
    $250$ & BENEDETTI JOËL \\
    \hline
    $191$ & BERGEAULT FRANÇOIS \\
    \hline
    $158$ & BERNARD MARTINE \\
    \hline
    $14$ & BERNARD SANDRINE \\
    \hline
    $188$ & BERNAT JEAN-MATTHIEU \\
    \hline
    $381$ & BERNINI SOPHIE \\
    \hline
    $193$ & BERREUR FLORENCE \\
    \hline
    $62$ & BERTHE VALÉRIE \\
    \hline
    $293$ & BERTRAND OLIVIER \\
    \hline
    $243$ & BEUNAICHE ÉRIC \\
    \hline
    $311$ & BIENAIMÉ LAURE \\
    \hline
    $128$ & BISCARAT JEAN-CLAUDE \\
    \hline
    $60$ & BLANC CHRISTOPHE \\
    \hline
    $275$ & BLANC VALÉRIE \\
    \hline
    $104$ & BOCHEZ SOPHIE \\
    \hline
    $109$ & BONDYFALAT GILLES \\
    \hline
    $323$ & BONI ISABELLE \\
    \hline
    $228$ & BONIFACE JACQUELINE \\
    \hline
    $109$ & BORDES VALÉRIE \\
    \hline
    $188$ & BORNAIS CLAIRE \\
    \hline
    $298$ & BORNSZTEIN PIERRE \\
    \hline
    $373$ & BOSC LAURENT \\
    \hline
    $31$ & BOSIO FRÉDÉRIC \\
    \hline
    $43$ & BOUCHER OLIVIER \\
    \hline
    $174$ & BOUCHERIE JEAN \\
    \hline
    $113$ & BOUTIN SAMUEL \\
    \hline
    $388$ & BOUTTIER PIERRICK \\
    \hline
    $351$ & BOUYGE LAURENCE \\
    \hline
    $213$ & BRAHIMI MOHAMED \\
    \hline
    $311$ & BREVART CLÉMENT \\
    \hline
    $216$ & BRIZAY ÉRIC \\
    \hline
    $76$ & BRUCHON VALÉRIE \\
    \hline
    $121$ & BRUNEAU VINCENT \\
    \hline
    $115$ & BUFF XAVIER \\
    \hline
    $115$ & BURAUX ÉP. BOURGEOIS BÉNÉDICTE \\
    \hline
    $388$ & BURGHGRAEVE ÉP. ZWERTVAEGHER KARINE \\
    \hline
    $211$ & BURGNARD JOËLLE \\
    \hline
    $78$ & BURIE JEAN-BAPTISTE \\
    \hline
    $51$ & BUSCA JÉRÔME \\
    \hline
    $403$ & BUSSEREAU NATHALIE \\
    \hline
    $367$ & BUSSON BENOIST \\
    \hline
    $275$ & CABADET THIERRY \\
    \hline
    $403$ & CABET AURORE \\
    \hline
    $139$ & CAMENEN ÉP. BERTRANE ANNIE \\
    \hline
    $339$ & CANTINEAU ÉP. CANTINEAU CHRISTINE \\
    \hline
    $3$ & CARBOU GILLES \\
    \hline
    $64$ & CARRIEU HERVÉ \\
    \hline
    $98$ & CAUBEL CLÉMENT \\
    \hline
    $213$ & CERISIER MARTIN \\
    \hline
    $323$ & CHAIX ÉP. PITZALIS FRANÇOISE \\
    \hline
    $69$ & CHAKROUN HEDI \\
    \hline
    $1$ & CHAMBERT-LOIR ANTOINE \\
    \hline
    $46$ & CHAMBRIS CHRISTINE \\
    \hline
    $133$ & CHAMPION ÉP. DUJARDIN ALINE \\
    \hline
    $319$ & CHAPPEY ÉDOUARD \\
    \hline
    $162$ & CHARRIER LUCIE \\
    \hline
    $153$ & CHARTON BRIGITTE \\
    \hline
    $169$ & CHARVET FRÉDÉRIC \\
    \hline
    $403$ & CHASTEL EMMANUEL \\
    \hline
    $298$ & CHAUMINE JEAN \\
    \hline
    $144$ & CHESNAU DOMINIQUE \\
    \hline
    $2$ & CHEVREL MARC \\
    \hline
    $7$ & CHOIMET DENIS \\
    \hline
    $298$ & CHOLLET JEAN \\
    \hline
    $56$ & CHONE PHILIPPE \\
    \hline
    $339$ & CLÉMENT LAURENCE \\
    \hline
    $95$ & CLOUTOT ANNE \\
    \hline
    $360$ & COLBEAU SOPHIE \\
    \hline
    $174$ & COLETTE MICHEL \\
    \hline
    $243$ & COLIN SYLVIE \\
    \hline
    $360$ & COMBEAU PASCAL \\
    \hline
    $367$ & COMBETTES LAURENCE \\
    \hline
    $73$ & CORDIER STÉPHANE \\
    \hline
    $200$ & CORRE AGNÈS \\
    \hline
    $319$ & COUPPEY PHILIPPE \\
    \hline
    $180$ & COURILLEAU PATRICK \\
    \hline
    $308$ & COVAREL HERVÉ \\
    \hline
    $45$ & COZAR LIONEL \\
    \hline
    $208$ & CRENN ISABELLE \\
    \hline
    $293$ & CREVISY HÉLÈNE \\
    \hline
    $7$ & CROCY PHILIPPE \\
    \hline
    $283$ & D'ANDRIA PIERRE \\
    \hline
    $275$ & DANEDE ISABELLE \\
    \hline
    $104$ & DARNIÈRE JACK-LUCK \\
    \hline
    $61$ & DARTYGE CÉCILE \\
    \hline
    $339$ & DAVID PHILIPPE \\
    \hline
    $216$ & DAVID ULRIC \\
    \hline
    $86$ & DE BRAUWERE ÉRICK \\
    \hline
    $293$ & DECRION MICHEL \\
    \hline
    $293$ & DELEBASSÉE ÉRIC \\
    \hline
    $89$ & DELEVAL PHILIPPE \\
    \hline
    $323$ & DELFAUD JACQUES \\
    \hline
    $210$ & DELGIOVINE SYLVIE \\
    \hline
    $381$ & DELQUIE HÉLÈNE \\
    \hline
    $35$ & DEMEUSOIS GILLES \\
    \hline
    $258$ & DENIAU ISABELLE \\
    \hline
    $172$ & DEPARIS ÉP. FRITSCH CORINNE \\
    \hline
    $180$ & DE SAINT-AUBERT EMMANUEL \\
    \hline
    $403$ & DESIDERI ANNE \\
    \hline
    $193$ & DESMIS CATHY \\
    \hline
    $264$ & DESRUELLES ÉP. BAHEUX CAROLE \\
    \hline
    $113$ & DESSET CARINE \\
    \hline
    $143$ & DESTEPHEN BRUNI \\
    \hline
    $43$ & DHERSIN JEAN-STÉPHANE \\
    \hline
    $250$ & DIAGNE MALICK \\
    \hline
    $268$ & DOR HENRI \\
    \hline
    $275$ & DORARD RICHARD \\
    \hline
    $115$ & DREYFUS JEAN-ÉRIC \\
    \hline
    $284$ & DRIF ABDELOUAHAB \\
    \hline
    $38$ & DUCASSE FLORENCE \\
    \hline
    $17$ & DUCHON PHILIPPE \\
    \hline
    $97$ & DUHEILLE FRÉDÉRIQUE \\
    \hline
    $319$ & DUMAS ETIENNE \\
    \hline
    $27$ & DU MOULIN RÉGIS \\
    \hline
    $348$ & DUPLESSIS LUC \\
    \hline
    $308$ & DUPRÉ ÉP. DURAND-WALLEZ VÉRONIQUE \\
    \hline
    $228$ & DUQUESNOY JEAN-MARC \\
    \hline
    $358$ & DURAND BRUNO \\
    \hline
    $159$ & DURAND PASCAL \\
    \hline
    $323$ & ELAZZAOUI RAOUL \\
    \hline
    $164$ & ELBHAR ALEXIS \\
    \hline
    $153$ & EMONET PASCAL \\
    \hline
    $333$ & ERARD FRÉDÉRIC \\
    \hline
    $63$ & ESMAN ROMUALD \\
    \hline
    $316$ & ESTIENNE LAURENCE \\
    \hline
    $79$ & EYCHENNE FRANÇOIS \\
    \hline
    $237$ & FAOUZI TAOUFIQ \\
    \hline
    $107$ & FARDOUN ALI \\
    \hline
    $193$ & FAURE JOËL \\
    \hline
    $128$ & FAURE NATHALIE \\
    \hline
    $339$ & FAURY ÉP. FAURY CHRISTINE \\
    \hline
    $335$ & FERRARI STÉPHANE \\
    \hline
    $82$ & FERRIÈRE RÉGIS \\
    \hline
    $123$ & FLOSSE ÉP. FOUCAUD MARIE-PIERRE \\
    \hline
    $373$ & FORT KARINE \\
    \hline
    $381$ & FOUQUAT VÉRONIQUE \\
    \hline
    $241$ & FRAISSEIX NOËL \\
    \hline
    $3$ & FRANCINOU SERGE \\
    \hline
    $109$ & FRAPPA AGNÈS \\
    \hline
    $293$ & FREMD CYRIL \\
    \hline
    $155$ & FREYDIER ODILE \\
    \hline
    $264$ & GAIGNE BERNARD \\
    \hline
    $18$ & GAJA FLORENCE \\
    \hline
    $339$ & GARNIER GHISLAINE \\
    \hline
    $247$ & GAUCHARD XAVIER \\
    \hline
    $74$ & GAURANT MAUD \\
    \hline
    $166$ & GAUTIER FRANCK \\
    \hline
    $29$ & GERMONI JÉRÔME \\
    \hline
    $10$ & GIANELLA HERVÉ \\
    \hline
    $221$ & GILLES CATHERINE \\
    \hline
    $56$ & GINOUILLAC STÉPHANE \\
    \hline
    $159$ & GIRAULT NATHALIE \\
    \hline
    $49$ & GIRY THOMAS \\
    \hline
    $403$ & GITZHOFER FRÉDÉRIQUE \\
    \hline
    $228$ & GOFFAUX OLIVIER \\
    \hline
    $388$ & GRAMMATICO VALÉRIE \\
    \hline
    $319$ & GRANGE LAURENT \\
    \hline
    $250$ & GRANIER EMMANUEL \\
    \hline
    $232$ & GRANIER HERVÉ \\
    \hline
    $33$ & GRENIE LOÏC \\
    \hline
    $3$ & GRENIER EMMANUEL \\
    \hline
    $166$ & GRENIER PIERRE \\
    \hline
    $103$ & GUÉRIN RICHARD \\
    \hline
    $335$ & GUERLOU CATHERINE \\
    \hline
    $20$ & GUILLERMOU STÉPHANE \\
    \hline
    $351$ & GUILLET CHRISTOPHE \\
    \hline
    $264$ & HABERKORN BRUNO \\
    \hline
    $206$ & HAGOPIAN CATHERINE \\
    \hline
    $25$ & HAMEL FRANÇOIS \\
    \hline
    $21$ & HAN FRÉDÉRIC \\
    \hline
    $56$ & HANNACHI GUILLAUME \\
    \hline
    $54$ & HANNACHI NICOLAS \\
    \hline
    $89$ & HANUS BORIS \\
    \hline
    $107$ & HASQUENOPH ÉP. BERNOU BRIGITTE \\
    \hline
    $367$ & HAUZE PIERRE \\
    \hline
    $128$ & HERBELOT ALAIN \\
    \hline
    $398$ & HERMET ISABELLE \\
    \hline
    $258$ & HERREMAN ALAIN \\
    \hline
    $200$ & HERRERA DENIS \\
    \hline
    $133$ & HESSE ÉP. LEPLEIX DANIÈLE \\
    \hline
    $323$ & HEUDRE NATHALIE \\
    \hline
    $298$ & HIVON LAURENT \\
    \hline
    $51$ & HOCQUENGHEM GILLES \\
    \hline
    $237$ & HORY FRANÇOISE \\
    \hline
    $18$ & HUBERT PASCAL \\
    \hline
    $360$ & HURIER CHRISTOPHE \\
    \hline
    $255$ & IAMARENE SAÏD \\
    \hline
    $186$ & IBBA JAAFAR \\
    \hline
    $323$ & IMMAS ABDELMJID \\
    \hline
    $208$ & INDAUD STÉPHANE \\
    \hline
    $403$ & ISEL STÉPHANE \\
    \hline
    $268$ & ISSERTY CHRISTOPHE \\
    \hline
    $211$ & JAECK FRÉDÉRIC \\
    \hline
    $139$ & JAILLET CHRISTOPHE \\
    \hline
    $268$ & JAMBON MARIANNE \\
    \hline
    $47$ & JAURY ALEXIS \\
    \hline
    $92$ & JEANJEAN JACQUES \\
    \hline
    $174$ & JOLAIS ALAIN \\
    \hline
    $168$ & JOUFFROY GÉRALDINE \\
    \hline
    $388$ & JUGNIOT THIERRY \\
    \hline
    $71$ & JULIEN ANNE-LAURE \\
    \hline
    $275$ & JUNTAS MICHEL \\
    \hline
    $275$ & KAYSER STÉPHANE \\
    \hline
    $323$ & KEITA IBRAHIM \\
    \hline
    $298$ & KERMARREC ÉP. HILI HÉLÈNE \\
    \hline
    $388$ & KIEFFER YVAN \\
    \hline
    $115$ & KOTECKI FRÉDÉRIC \\
    \hline
    $3$ & KOWALSKI EMMANUEL \\
    \hline
    $400$ & KYRIACOPOULOS LAURENT \\
    \hline
    $360$ & LACOUTURE ALAIN \\
    \hline
    $268$ & LACRESSE CHRISTELLE \\
    \hline
    $403$ & LA FONTAINE FRANÇOIS \\
    \hline
    $36$ & LAIGNEAU FRÉDÉRIC \\
    \hline
    $351$ & LAINEY JEAN \\
    \hline
    $289$ & LAISI ANDRÉ \\
    \hline
    $213$ & LANGNY CÉLINE \\
    \hline
    $136$ & LARRIBAU OLIVIER \\
    \hline
    $49$ & LARROUY HÉLÈNE \\
    \hline
    $358$ & LASSOUS MARIE \\
    \hline
    $335$ & LATAILLADE SOPHIE \\
    \hline
    $136$ & LATHELIZE ARNAUD \\
    \hline
    $323$ & LATOURNERIE STÉPHANE \\
    \hline
    $323$ & LAU HYACINTHE \\
    \hline
    $233$ & LAUBACHER DIDIER \\
    \hline
    $403$ & LAUR JEAN-FRANÇOIS \\
    \hline
    $51$ & LAURON PHILIPPE \\
    \hline
    $241$ & LAUVAUX ÉP. LAUVAUX CHRISTINE \\
    \hline
    $82$ & LAUZERAL CHRISTINE \\
    \hline
    $298$ & LAVAYSSE NICOLAS \\
    \hline
    $36$ & LE BORGNE STÉPHANE \\
    \hline
    $247$ & LECLERCQ ANNE-CHRISTINE \\
    \hline
    $333$ & LE FLOCH GAËLLE \\
    \hline
    $221$ & LE GALLAIS SYLVIE \\
    \hline
    $186$ & LEGRAS ÉP. CHARTIER-KASTLE ANNE-ISABELLE \\
    \hline
    $339$ & LEHEBEL PATRICK \\
    \hline
    $193$ & LEMOINE JEAN-LUC \\
    \hline
    $56$ & LÉON CHRISTOPHE \\
    \hline
    $193$ & LEPAGE MARIE-CHRISTINE \\
    \hline
    $193$ & LEPETZ DOMINIQUE \\
    \hline
    $237$ & LE POULIGUEN MARC \\
    \hline
    $193$ & LEROUX VALÉRIE \\
    \hline
    $395$ & LEROY VINCENT \\
    \hline
    $80$ & LESPINE NATHALIE \\
    \hline
    $268$ & LETARD PASCAL \\
    \hline
    $388$ & LIÉNARD ÉP. FABRY DOMINIQUE \\
    \hline
    $10$ & LOMBARDI ERIC \\
    \hline
    $123$ & LORAUD NATHALIE \\
    \hline
    $102$ & LORENZON PIERRE \\
    \hline
    $289$ & LUCARONI SABINE \\
    \hline
    $348$ & LUCAS VALÉRIE \\
    \hline
    $403$ & LUGARDON VALÉRIE \\
    \hline
    $89$ & LUKOWICZ VALÉRIE \\
    \hline
    $308$ & MAFFRE RÉMI \\
    \hline
    $400$ & MAHLER ADRIEN \\
    \hline
    $169$ & MAIRE CHRISTIAN \\
    \hline
    $395$ & MAIRESSE SOPHIE \\
    \hline
    $221$ & MALBERT EVELYNE \\
    \hline
    $287$ & MALHERBE XAVIER \\
    \hline
    $184$ & MARCHAND MICHEL \\
    \hline
    $191$ & MARCOU CAROLE \\
    \hline
    $216$ & MAREST FRANÇOIS \\
    \hline
    $243$ & MAROT MARIE-LAURE \\
    \hline
    $221$ & MARTIN PATRICIA \\
    \hline
    $388$ & MARTINOT PIERRE \\
    \hline
    $82$ & MASSE ERIC \\
    \hline
    $373$ & MASSON GENEVIÈVE \\
    \hline
    $95$ & MAURICE-BOKANOW OLIVER \\
    \hline
    $360$ & MAURS ÉP. MIGNONAT NATHALIE \\
    \hline
    $233$ & MEGARBANE NAIM \\
    \hline
    $81$ & MENEVIS HERVÉ \\
    \hline
    $351$ & MENGUY JEAN \\
    \hline
    $69$ & MEREL SANDRINE \\
    \hline
    $34$ & MERKER JOËL \\
    \hline
    $381$ & MERLE ÉP. LE KER MARIE \\
    \hline
    $139$ & METATIDJ SOPHIE \\
    \hline
    $100$ & METZ VINCENT \\
    \hline
    $351$ & MEYER ÉP. PIERRON DE MOND PATRICIA \\
    \hline
    $298$ & MICHEL JEAN-CHRISTOPHE \\
    \hline
    $13$ & MICHEL PHILIPPE \\
    \hline
    $7$ & MIGNON THIERRY \\
    \hline
    $339$ & MOENECLAEY PHILIPPE \\
    \hline
    $381$ & MOINE CLAIRE \\
    \hline
    $138$ & MOINIER STÉPHANE \\
    \hline
    $64$ & MOISAN LIONEL \\
    \hline
    $148$ & MOLLARET JÉRÔME \\
    \hline
    $109$ & MONCORGÉ DOMINIQUE \\
    \hline
    $68$ & MONNIAUX SYLVIE \\
    \hline
    $221$ & MOREL SONIA \\
    \hline
    $237$ & MORINEAU CHRISTOPHE \\
    \hline
    $221$ & MORIZOT ÉP. BARTHOD LYDIA \\
    \hline
    $126$ & MOSTAFA EL GRAOUI EL \\
    \hline
    $367$ & MULLER PIERRE-ALAIN \\
    \hline
    $115$ & MUNCH ANNICK \\
    \hline
    $29$ & NGUYEN DINH AN PASCALE \\
    \hline
    $127$ & NOIREL LAURENT \\
    \hline
    $188$ & NOQUET CAROLINE \\
    \hline
    $403$ & NOUEL CHRISTINE \\
    \hline
    $144$ & OBRECHT CHRISTIAN \\
    \hline
    $133$ & OMARJEE MOUBINOOL \\
    \hline
    $284$ & ORIEUX NATHALIE \\
    \hline
    $162$ & OUAFDEL ALI \\
    \hline
    $85$ & OYONO HERVÉ \\
    \hline
    $298$ & PARIZOT HERVÉ \\
    \hline
    $243$ & PÉLISSIÉ DE MON DANIEL \\
    \hline
    $381$ & PELLIER FRANCK \\
    \hline
    $316$ & PELLISSIER FLORE \\
    \hline
    $100$ & PERGENT ÉP. HARDMEIER PASCALE \\
    \hline
    $144$ & PERRET LINE \\
    \hline
    $298$ & PICARD CLAUDE \\
    \hline
    $139$ & PILLOT MICHEL \\
    \hline
    $98$ & PINCET FRÉDÉRIC \\
    \hline
    $247$ & PINON CAROLE \\
    \hline
    $237$ & POGU FRANCK \\
    \hline
    $289$ & POIROT VÉRONIQUE \\
    \hline
    $287$ & PRADEAU PATRICK \\
    \hline
    $200$ & PRIMET PIERRE \\
    \hline
    $268$ & PROAL HUBERT \\
    \hline
    $67$ & QUEGUINER ANNE \\
    \hline
    $268$ & RAGON EMMANUEL \\
    \hline
    $216$ & RAIMOND OLIVIER \\
    \hline
    $15$ & RAKOTONIAINA CÉLESTIN \\
    \hline
    $395$ & RAZANAMELSON JEAN-BAPTISTE \\
    \hline
    $41$ & REBER LAURENT \\
    \hline
    $298$ & REGNEAULT GEORGES \\
    \hline
    $150$ & RENARD ISABELLE \\
    \hline
    $311$ & ROBINET NATHALIE \\
    \hline
    $351$ & RODRIGUEZ FRÉDÉRIC \\
    \hline
    $38$ & ROESCH MICHEL-DENIS \\
    \hline
    $284$ & ROGEON PHILIPPE \\
    \hline
    $250$ & ROMAIN GINOU \\
    \hline
    $311$ & ROUAULT ÉP. HERVÉ LAURENCE \\
    \hline
    $264$ & ROUSSEAU GWENAELLE \\
    \hline
    $403$ & ROUSSELOT THIERRY \\
    \hline
    $162$ & ROZE ALAIN \\
    \hline
    $284$ & RUETSCH PIERRE \\
    \hline
    $255$ & RUF SYLVIE \\
    \hline
    $106$ & RUIZ HÉLÈNE \\
    \hline
    $21$ & RUIZ JEAN \\
    \hline
    $168$ & SAFI MOUNIR \\
    \hline
    $74$ & SAINT-LOUBERT ERWAN \\
    \hline
    $120$ & SALAUN FRANÇOIS \\
    \hline
    $233$ & SALLE VÉRONIQUE \\
    \hline
    $174$ & SANDOZ CATHERINE \\
    \hline
    $373$ & SAUSSAY GABRIEL \\
    \hline
    $233$ & SAVATIER FABRICE \\
    \hline
    $316$ & SCHAFFAR ÉP. MAILLARD ALEXANDRA \\
    \hline
    $323$ & SCHERMESSER VÉRONIQUE \\
    \hline
    $258$ & SCHLEININGER CHRISTELLE \\
    \hline
    $403$ & SCHMENK CAROLE \\
    \hline
    $339$ & SCHMUTZ DAVID \\
    \hline
    $275$ & SICE FRÉDÉRIC \\
    \hline
    $42$ & SIEFERT MARIE-DOMINIQUE \\
    \hline
    $48$ & SLAMA YAACOB \\
    \hline
    $121$ & SMETS JEAN-PAUL \\
    \hline
    $250$ & SOAVI VALÉRIE \\
    \hline
    $360$ & STEPHANN JEAN \\
    \hline
    $275$ & STRAUB ODILE \\
    \hline
    $148$ & STRAUSS JEAN-PAUL \\
    \hline
    $381$ & SURREL PHILIPPE \\
    \hline
    $16$ & TAIEB FRANCK \\
    \hline
    $125$ & TAMISIER FRÉDÉRIC \\
    \hline
    $180$ & TANGUY PIERRE \\
    \hline
    $128$ & TEISSEYRE ÉP. LEFIN MURIEL \\
    \hline
    $76$ & TENTI MARC \\
    \hline
    $373$ & THERME PATRICIA \\
    \hline
    $398$ & THOUVENEL HERVÉ \\
    \hline
    $64$ & THUILLAS MARTINE \\
    \hline
    $150$ & TONNEAU HUBERT \\
    \hline
    $335$ & TOSCANO FLORENCE \\
    \hline
    $10$ & UHRES JOHANN \\
    \hline
    $174$ & VALLON-HOARAU JEAN-PIERRE \\
    \hline
    $174$ & VANDENDRIESSCHE ERIC \\
    \hline
    $150$ & VARGAS CYRIL \\
    \hline
    $21$ & VARJABEDIAN SERGE \\
    \hline
    $26$ & VAUDENAY SERGE \\
    \hline
    $164$ & VAUTHIER LAURENT \\
    \hline
    $155$ & VERDOUCQ ÉP. KLING STÉPHANIE \\
    \hline
    $71$ & VERNE CATHERINE \\
    \hline
    $92$ & VERNHET LAURENT \\
    \hline
    $159$ & VIALARET PASCAL \\
    \hline
    $403$ & VIAU ANNE \\
    \hline
    $373$ & VIGNAULT JEAN-PAUL \\
    \hline
    $311$ & VIGNE MAGALI \\
    \hline
    $184$ & VILLE PASCAL \\
    \hline
    $180$ & VINCENT CLAUDE \\
    \hline
    $221$ & VINCENT-LANCRIN CÉDRIC \\
    \hline
    $373$ & VIVIEN FRÉDÉRIC \\
    \hline
    $40$ & WATBLED FRÉDÉRIQUE \\
    \hline
    $172$ & WEBER ÉP. DUBRAC LUCILE \\
    \hline
    $258$ & WERNER CORINNE-EVE \\
    \hline
    $373$ & WIECZOREK MYRIAM \\
    \hline
    $348$ & WIRIG GILLES \\
    \hline
    $289$ & YASSAI SADR \\
    \hline
    $28$ & ZAMORA PHILIPPE \\
    \hline
  \end{xltabular}

  \begin{flushright}
    {\tiny Source : \url{http://nicolas.martin.ens.free.fr/agreg/1992.html}}
  \end{flushright}
  %</content>
\end{document}
